---
title: "iteration"
author: "Anyu Zhu"
date: "11/4/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
```

## Z scores
```{r}
x_vec = rnorm(25, mean = 5, sd = 4)
(x_vec - mean(x_vec)) / sd(x_vec)

z_scores = function(x){
  z = (x - mean(x)) / sd(x)
  return(z)
}

z_scores(x = x_vec)

y_vec = rnorm(40, mean = 12, sd = 0.3)
z_scores(y_vec)
```

```{r, error = TRUE}
z_scores = function(x){
  if (!is.numeric(x)){
    stop("x needs to be numeric")
  }
  
  if (length(x) < 3){
    stop("x should have at least 3 numbers")
  }
  
  z = (x - mean(x)) / sd(x)
  return(z)
}

z_scores(c("a", "b", "c", "d"))
z_scores(3)
z_scores(mtcars)
```

## Multiple outputs
```{r}
mean_and_sd = function(x){
  if (!is.numeric(x)){
    stop("x needs to be numeric")
  }
  
  if (length(x) < 3){
    stop("x should have at least 3 numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  output_df = 
    tibble(mean = mean_x,
           sd = sd_x)
  
  return(output_df)
}

mean_and_sd(x_vec)
mean_and_sd(y_vec)
```

## Different sample sizes, means, sds
```{r}
sim_data = 
  tibble(
    x = rnorm(30, mean = 2, sd = 3)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
```

function that simulates data, compute mean and sd.
```{r}
sim_mean_sd = function(n, mu, sigma){
  sim_data = 
  tibble(
    x = rnorm(n, mean = mu, sd = sigma)
  )

  sim_data %>% 
    summarize(
      mean = mean(x),
      sd = sd(x)
    )
}

sim_mean_sd(30, 4, 3)
```

## Napoleon dynamics
```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_elements(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_elements("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = 
  dynamite_html %>%
  html_elements(".review-text-content span") %>%
  html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

Write a function gets reviews based on page url
```{r}
get_page_reviews = function(page_url){
  
  page_html = read_html(page_url)

  review_titles = 
    page_html %>%
    html_elements(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    page_html %>%
    html_elements("#cm_cr-review_list .review-rating") %>%
    html_text()
  
  review_text = 
    page_html %>%
    html_elements(".review-text-content span") %>%
    html_text()
  
  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
  
  return(reviews)
}

base_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
urls = str_c(base_url, 1:5)

bind_rows(
  get_page_reviews(urls[1]),
  get_page_reviews(urls[2]),
  get_page_reviews(urls[3]),
  get_page_reviews(urls[4]),
  get_page_reviews(urls[5]))
```

## Lists
```{r}
l = list(
  vec_numeric = 5:8,
  vec_logical = c(TRUE, FALSE),
  summary = summary(rnorm(1000, mean = 5, sd = 3))
)

l[[3]]

l[["summary"]]
```

## List of normals
```{r}
list_norms = 
  list(
    a = rnorm(50, mean = 2, sd = 1),
    b = rnorm(50, mean = 5, sd = 3),
    c = rnorm(50, mean = 10, sd = 1.5),
    d = rnorm(50, mean = -8, sd = 4)
  )

mean_and_sd(list_norms[[1]])
```

## for loop

to iterate over the list of normals
```{r}
output = vector("list", length = 4)

for (i in 1:4){
  output[[1]] = mean_and_sd(list_norms[[1]])
}
```

use map:

```{r}
output = map(list_norms, mean_and_sd)

output_2 = map(list_norms, summary)
```

## List Columns
```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    norms = list_norms
  )

listcol_df %>% pull(name)
listcol_df %>% pull(norms)
listcol_df %>% filter(name == "a")

listcol_df %>% 
  mutate(summaries = map(listcol_df$norms, mean_and_sd))
```

## Nested data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Nest data within location

```{r}
weather_nested = nest(weather_df, data = date:tmin)

unnest(weather_nested, data)

weather_nested %>% pull(data)

lm(tmax ~ tmin, data = weather_nested$data[[3]])

weather_lm = function(df){
  lm(tmax ~ tmin, data = df)
}

weather_lm(weather_nested$data[[1]])

map(weather_nested$data, weather_lm)

weather_nested %>% 
  mutate(lm_results = map(data, weather_lm))
```

## Napoleon

```{r}
map(urls, get_page_reviews)

napoleon_df = tibble(
  urls = urls
)

napoleon_df %>% 
  mutate(reviews = map(urls, get_page_reviews)) %>% 
  select(reviews) %>% 
  unnest()
```

Simulation

start with a for loop
```{r}
output = vector("list", length = 100)

for (i in 1:100){
  output[[i]] = sim_mean_sd(30, 3, 4)
}

bind_rows(output)
```

use a loop function
```{r}
sim_results = 
  rerun(100, sim_mean_sd(30, 3, 4)) %>% 
  bind_rows()
```

look at results
```{r}
sim_results %>% 
  ggplot(aes(x = mean)) + geom_density()

sim_results %>% 
  summarize(
    avg_sample_mean = mean(mean),
    ad_samp_mean = sd(mean)
  )

sim_results %>% 
  ggplot(aes(x = sd)) + geom_density()
```




